Using Big Data for Music Synthesis

### 2013-05-09 writeup/paper.tex
adding some more information relating to secondary sorting

\usepackage{listings}
\lstloadlanguages{Ruby}
\lstset{
basicstyle=\ttfamily\color{black},
commentstyle = \ttfamily\color{red},
keywordstyle=\ttfamily\color{blue},
stringstyle=\color{orange}}

@@

\paragraph{Motivation}

@@

\paragraph{The HSV format}

@@

\paragraph{Generating music}
\label{sec:generating}

@@

\paragraph{Conversion to colors}

@@

@@

After taking the image data to an intermediate format, we must map the
image data to a set of note / region pairs for use in the MIDI.  To do
this, we do projection

\paragraph{Mixing and producing playable music}

>>>>

\usepackage{listings}
\lstloadlanguages{Ruby,Java}
\lstset{
basicstyle=\ttfamily\color{black},
commentstyle = \ttfamily\color{red},
keywordstyle=\ttfamily\color{blue},
stringstyle=\color{orange}}

@@

\subsection{Motivation}

@@

\subsection{The HSV format}

@@

\subsection{Generating music}
\label{sec:generating}

@@

We represent each region of the image by a representative color, which
is obtained (as noted previously) using thumbnailing.

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{image1}
  \caption{A subfigure}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{image1}
  \caption{A subfigure}
  \label{fig:sub2}
\end{subfigure}
\caption{A figure with two subfigures}
\label{fig:test}
\end{figure}

@@

Our implementation for this conversion happens in the
\code{WriteImagesToSequenceFile} class.  They key novelty in this
class is the conversion of image data to a \code{SequenceFile} based
representation.  A \code{SequenceFile} works well for our application
because we need to stream potentially large amounts of image data (raw
bytes).  This is fundamentally no different than creating a custom
Writable instance to serialize to a \code{SequenceFile} at a later
point, but given the simplicity of our representation we say no need
to do this.

\begin{figure}
\begin{lstlisting}[language=Java]
public class WriteImagesToSequenceFile {
  BufferedImage img = null;
  SequenceFile.Writer writer = null;
  FileSystem fs = FileSystem.get(conf);

  FileStatus[] fss = 
    fs.globStatus(new Path(inputPath 
      + "/*.jpg"));

  writer = SequenceFile.createWriter(fs, 
    conf, outPath, IntWritable.class,
    ArrayListOfIntsWritable.class);
  int counter = 0;
  for (FileStatus status : fss) {
    IntWritable image_counter = 
      new IntWritable();
    ArrayListOfIntsWritable 
      pixelData = 
        new ArrayListOfIntsWritable();

    img = ImageIO.read(
      new File(status.getPath()
               .toString().substring(5)));

    // Get the RBG integer for each pixel 
    // in 3X3
    for(int j = 0; j < thumbs; j++) {
      for(int i = 0; i< thumbs; i++) {
        pixelData.add(img.getRGB(i,j));
      }
    }

    // Write to the sequence file
    image_counter.set(counter);
    writer.append(image_counter, pixelData);
    counter += 1;
  } 
}
\end{lstlisting}
\caption{Snippet of code from \code{WriteToSequenceFile} showing
  format used in sequence files throughout the MapReduce jobs.}
\end{figure}

@@

After taking the image data to an intermediate format, we must map the
image data to a set of note / region pairs for use in the MIDI.  To do
this, we map a conversion function across each of the different
portions of each image.  The conversion happens by mapping over our
set of images in the \code{Image2MusicMR} class.  The output of the
image to music conversion is $n$ sets of note lists (where notes are
expressed as pairs).

The strategy used in the conversion is to map over each pixel in an
image, apply the conversion function, and emit it to a reducer to
collate together.  After mapping over each pixel, we need to end up
with a stream of images for each region: a naive implementation simply
maps each pixel in our input corpus to these tone, velocity pairs:

\[
  map : id \times (r,g,b) \to region \times (tone \times velocity)
\]

However, when we actually mix the music, we need each of the streams
to be in an ordered format.  Because the default sorting order does
not take this into account, the music ends up jumbled (each of the
regions is permuted with respect to input ID in an arbitrary way).  To
fix this, we perform secondary sorting on the input ID:

\[
  map : id \times (r,g,b) \to (id \times region) \times (tone \times velocity)
\]

\subsection{Mixing and producing playable music}
